Bucket-Sorted Independent Sets for Algebraic Multigrid

### 2007-08-24 bsis_paper/paper.tex
* Section 2 updates and new content.
git-svn-id: file:///home/rblake/svn/pamg/trunk@19 c7f3fe13-8c30-0410-9127-9a9c42fe009c

\subsection{Independent Set-Based Selection}
\label{sec:indep-set-based}
Independent set-based coarse grid selection algorithms rely on
\emph{strength of connection} measures to ascertain the influence
between unknowns.

>>>>

\subsection{Independent Set-Based Selection}
\label{sec:indep-set-based}
Independent set-based coarse grid selection algorithms implement three
routines to select coarse grids: initialization, independent set
selection, and weight update. A general independent-set based
coarsening algorithm is shown in
Algorithm~\ref{alg:general-indep-set}.
\begin{lstlisting}[caption={Independent Set-Based Coarse Grid
Selection},label=alg:general-indep-set]
%\textsc{Indep-Set-Coarse-Grid-Selection}$(\Omega)$:%
$F \leftarrow \emptyset$
$C \leftarrow \emptyset$
$w \leftarrow\,$%\textsc{Initialize-Weights}$(\Omega)$%
while $\Omega \ne \emptyset$
   $D \leftarrow\,$%\textsc{Select-Indep-Set}$(w,\, \Omega)$%
   $(F,\, C,\, \Omega,\, w) \leftarrow\,$%\textsc{Update-Weights}$(F,\,
                                C,\, \Omega,\, w)$%
end
\end{lstlisting}

Each vertex in the graph is assigned a weight based on its merit to
becoming a $C$-point. The largest weights are conferred to vertices
best suited to become $C$-points. The quality of potential $C$-points
is quantified by \emph{strength of connection} measures. The classical
strength of connection measure is based entirely on the relative sizes
of off-diagonal nonzeros in $A$. In the classical definition, the set
of unknowns that unknown $i$ strongly depends upon is defined as
\begin{equation}
\label{2:eqn:S_i}
S_i = \left\{j: i \ne j \textrm{ and }|a_{ij}| \ge \theta \max_{k \ne
i}|a_{ik}|\right\},
\end{equation}
where $a_{ij}$ is the nonzero in row $i$, column $j$ of matrix $A$ and
$0 < \theta \le 1$. The set of unknowns that $i$ strongly influences,
denoted $S_i^T$, is defined as the set of unknowns that strongly
depend on $i$: $S_i^T = \{j: i \in S_j\}$.

This classical strength definition is formulated based on M-matrix
properties and does not model the influence between unknowns in
general cases. The formulation of new, effective, and inexpensive
strength of connection measures is an active area of
research~\cite{Brannick2005} and has the potential to extend the
applicability of AMG solvers.

Vertex $i$ is eligible to be added to the independent set $D$ if the
following condition is satisfied:
\begin{equation}
  \label{eq:D-selection}
  w_i > w_j,\, \forall j \in S_i \cup S_i^T.
\end{equation}
